No need to know: astrophysics-agnostic gravitational wave cosmology

### 2024-03-11 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[]{aastex631}
\usepackage{showyourwork}
\usepackage{macros}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{acro}
\acsetup{patch/longtable=false}

@@

We have also predicted a \variable{output/nonparh0percent.txt}\% measurement of \Ho{} by the end of \ac{O5} using non-parametric spectral sirens.
A similar study with parametric methods \citep{Chen:2024gdn} predicts an \result{X\%} measurement, demonstrating a \result{negligible/substantial/marginal} increase in precision.
However, the true population of compact objects in the Universe is unknown.
It is therefore impossible to know the true functional form of the mass distribution, so systematic uncertainties arising from an incorrect choice for the form of the mass distribution are inevitable.
With current observations, these systematic effects are dwarfed by statistical uncertainties.
However, next-generation detectors will herald in enough \ac{GW} observations to substantially decrease statistical uncertainty in these measurements: \citet{pierra_study_2023} show that incorrect assumptions about the shape of the mass distribution can lead to \result{$\sim3\sigma$} systematic biases in \Ho when catalogs contain 2,000 events.
Thus, the additional statistical uncertainty introduced by non-parametric approaches may be preferable to the systematic errors associated with choosing a parametric model.

>>>>

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{macros}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{acro}
\acsetup{patch/longtable=false}

@@

We have also predicted a \variable{output/nonparh0percent.txt}\% measurement of \Ho{} by the end of \ac{O5} using non-parametric spectral sirens.
A similar study with parametric methods \citep{Chen:2024gdn} predicts an \result{X\%} measurement, demonstrating a \result{negligible/substantial/marginal} increase in precision.
However, the true population of compact objects in the Universe is unknown.
It is therefore impossible to know the true functional form of the mass distribution, so systematic uncertainties arising from an incorrect choice for the form of the mass distribution are inevitable.
With current observations, these systematic effects are dwarfed by statistical uncertainties.
However, next-generation detectors will herald in enough \ac{GW} observations to substantially decrease statistical uncertainty in these measurements: \citet{pierra_study_2023} show that incorrect assumptions about the shape of the mass distribution can lead to \result{$\sim3\sigma$} systematic biases in \Ho when catalogs contain 2,000 events, though this bias may be an over-estimate as it does not include measurement uncertainty of \ac{GW} parameters.
Thus, the additional statistical uncertainty introduced by non-parametric approaches may be preferable to the systematic errors associated with choosing a parametric model.
